---
title: "Homework_Week_6"
author: "Arora"
date: "October 23, 2017"
output: html_document
---
```Z.prop.test <- function(p1, n1, p0, p2, n2, alternative = "two.tailed", conf.level = 0.975, k=1000){
    p<-rep(NA,k)
    for (i in 1:k){
      p1
      n1
      p0
      conf.level<-0.975
      p2<-NULL
      n2<-NULL
      alpha=0.05
      Z <- p2-p1/(sqrt((p0)*(1-p0)*((1/n1)+(1/n2))))
      alternative<-"two tailed"

    if (alternative == "less") {
            p[i] <- pnorm(z, lower.tail = TRUE)  # calculates the associated p value
            hyp <- "p1 < p0"
        }
        if (alternative == "greater") {
            p[i] <- pnorm(z, lower.tail = FALSE)
            hyp <- "p1 > p0"
        }
        if (alternative == "two.tailed") {
            if (z > 0) {
                p[i] <- 2 * pnorm(z, lower.tail = FALSE)
            }
            if (z < 0) {
                p[i] <- 2 * pnorm(z, lower.tail = TRUE)
            }
      
    if (p2 == is.NULL) {
      Z=(p1-p0)/sqrt((p0*(1-p0))/n1)
    }
     if (alternative == "less") {
            p[i] <- pnorm(z, lower.tail = TRUE)  # calculates the associated p value
            hyp <- "p1 < p0"
        }
        if (alternative == "greater") {
            p[i] <- pnorm(z, lower.tail = FALSE)
            hyp <- "p1 > p0"
        }
        if (alternative == "two.tailed") {
            if (z > 0) {
                p[i] <- 2 * pnorm(z, lower.tail = FALSE)
            }
            if (z < 0) {
                p[i] <- 2 * pnorm(z, lower.tail = TRUE)
            }
      
    if (n2 == is.NULL) {
     Z=(p1-p0)/sqrt((p0*(1-p0))/n1) 
    }
     if (alternative == "less") {
            p[i] <- pnorm(z, lower.tail = TRUE)  # calculates the associated p value
            hyp <- "p1 < p0"
        }
        if (alternative == "greater") {
            p[i] <- pnorm(z, lower.tail = FALSE)
            hyp <- "p1 > p0"
        }
        if (alternative == "two.tailed") {
            if (z > 0) {
                p[i] <- 2 * pnorm(z, lower.tail = FALSE)
            }
            if (z < 0) {
                p[i] <- 2 * pnorm(z, lower.tail = TRUE)
            }
      }
    }
  }

      alpha=0.05
      critical.value<-qnorm(1-alpha/2)
      p1.CI<-((p1*(1-p1))/n1)
      p2.CI<-((p2*(1-p2))/n2)
      SE=sqrt(p1.CI+p2.CI)
      addition<-(p1+p2)+(critical.value*SE)
      addition
      subtraction<-(p1+p2)-(critical.value*SE)
      subtraction
      CI<-c(subtraction, addition)
  

      #p is the probability of the sucess where s=1 and failure = 0
    p<-p1 #isn't that what the probability proportion is?
    n1 #this is the number of trials run
    if(n1*p1<5) {
        "Warning: the input does not allow for normality to be assumed"
    }
    if(n1*(1*p1)<5) {"Warning: the input does not allow for normality to be assumed"
    ##I didn't know which n and p where referred in this particular part of the homework so I used n1 and p1 because that seemed most logical
    }

return(list(Z, p[i], CI)
    #this does not return anything except for the p[i] value and I have tried running the component parts of this and they work. I've tried moving curly brackets and that doesn't seem to be the problem.
}
```


```{r}
library(curl)
library(ggplot2)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/KamilarAndCooperData.csv")
d2 <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
d<-na.omit(d2)
#I removed na points because I could not do calculations without it
head(d)
```
```{r}
plot(data=d,Brain_Size_Species_Mean ~ MaxLongevity_m)
g<-ggplot(data=d, aes(x=Brain_Size_Species_Mean, y=MaxLongevity_m))
g<-g+geom_point()
g<-g+geom_smooth(method="lm", formula=y~x)
g
v<-data.frame(d)
lm_eqn = function(v){
    m = lm(y ~ x, v);
    eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
         list(a = format(coef(m)[1], digits = 2), 
              b = format(coef(m)[2], digits = 2), 
             r2 = format(summary(m)$r.squared, digits = 3)))
    as.character(as.expression(eq));                 
}
eq <- ddply(v,.(Brain_Size_Species_Mean),lm_eqn)
g<-g+geom_text(data=eq,label=lm_eqn(v), parse=TRUE)
g
#I haven't yet figured out how to label the equation; my current error says that the within the function, MaxLongevity could not be found
```


```{r}
m <- lm(data = d, Brain_Size_Species_Mean ~ MaxLongevity_m)

SSY <- sum((m$model$Brain_Size_Species_Mean - mean(m$model$Brain_Size_Species_Mean))^2)  # height - mean(height)
SSY

SSR <- sum((m$fitted.values - mean(m$model$Brain_Size_Species_Mean))^2)  # predicted height - mean height
SSR

SSE <- sum((m$model$Brain_Size_Species_Mean - m$fitted.values)^2)  # height - predicted height
SSE

df_regression <- 1
df_error <- 998
df_y <- 999
MSR <- SSR/df_regression
MSE <- SSE/df_error
MSY <- SSY/df_y

fratio <- MSR/MSE
fratio

rsquared <- SSR/SSY
rsquared
rho <- sqrt(rsquared)
rho

SSX <- sum((m$model$Brain_Size_Species_Mean - mean(m$model$Brain_Size_Species_Mean))^2)
SEbeta1 <- sqrt(MSE/SSX)
SEbeta1

#the standard error of the intercept, Beta naught is
SEbeta0 <- sqrt((MSE * sum(m$model$Brain_Size_Species_Mean^2))/(1000 * SSX))
SEbeta0

#It's very strange the beta one does not equal the intercept as given in the summary below which makes me think that I've done something wrong however I have copied this straight from the module 13 so I don't know what's up. 
```

```{r}
fit<-lm(d$Brain_Size_Species_Mean~d$MaxLongevity_m)
summary(fit)
#the Beta value is 0.1158 and the p value is 2.176e-05
```
#p value is less than alpha so reject β1

```{r}
ci<-predict(fit, newdata = data.frame(Brain_Size_Species_Mean = d$Brain_Size_Species_Mean), interval="confidence", level=0.90)
h_hat <- predict(fit, newdata = data.frame(Brain_Size_Species_Mean = d$Brain_Size_Species_Mean))
df <- data.frame(cbind(d$Brain_Size_Species_Mean, d$MaxLongevity_m, h_hat))
names(df) <- c("x", "y", "yhat")
head(df)
g <- ggplot(data = df, aes(x = Brain_Size_Species_Mean, y = yhat))
```
```{r}
df <- cbind(df, ci)
names(df) <- c("x", "y", "yhat", "CIfit", "CIlwr", "CIupr")
head(df)
```

```{r}
g <- ggplot(data = df, aes(x = x, y=y))+geom_line(aes(y=CIfit, colour = "CIfit")) + geom_line(aes(y=CIlwr, colour = "CIlwr")) +geom_line(aes(y=CIupr, colour = "CIupr")) + scale_colour_manual("",values=c("CIfit" = "black", "CIupr"="blue", "CIlwr"="pink")) + xlab(" ")
g <- g + geom_point(alpha = 1/2)
g
```

  scale_colour_manual("", 
                      breaks = c("TempMedia", "TempMax", "TempMin"),
                      values = c("TempMedia"="green", "TempMax"="red", 
                                 "TempMin"="blue")) +
  xlab(" ") +
  scale_y_continuous("Temperatura (C)", limits = c(-10,40)) + 
  labs(title="TITULO")

```{r}
g<-lm(df)
pi <- predict(g, newdata = data.frame(Mean_Brain_Size_Species = 800), interval = "prediction", 
    level = 0.90)  # for a single value
#I converted the dataframe df into a lm() but it not does not work because it cannot find yhat even though yhat has been defined above.  
```

```{r}
plot(data=d, log(Brain_Size_Species_Mean) ~ log(MaxLongevity_m))
g<-ggplot(data=d, aes(x=log(Brain_Size_Species_Mean), y=log(MaxLongevity_m)))
g<-g+geom_point()
g<-g+geom_smooth(method="lm", formula=y~x)
g
v<-data.frame(d)
lm_eqn = function(v){
    m = lm(y ~ x, v);
    eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
         list(a = format(coef(m)[1], digits = 2), 
              b = format(coef(m)[2], digits = 2), 
             r2 = format(summary(m)$r.squared, digits = 3)))
    as.character(as.expression(eq));                 
}
eq <- ddply(v,.(Brain_Size_Species_Mean),lm_eqn)
g<-g+geom_text(data=eq,label=lm_eqn(v), parse=TRUE)
g
#I haven't yet figured out how to label the equation; my current error says that the within the function, MaxLongevity could not be found
a<-log(d$Brain_Size_Species_Mean)
b<-log(d$MaxLongevity_m)
```
```{r}
fit<-lm(data=d,a~b)
summary(fit)
# beta1 value here is 0.4943 and the p value is 0.0004583 and the alpha is 0.1 and so again we reject the null that beta1 = 0
```
```{r}
ci<-predict(fit, newdata=data.frame(a), interval="confidence", level=0.90)
h_hat <- predict(fit, newdata = data.frame(a = a))
df <- data.frame(cbind(a, b, h_hat))
names(df) <- c("x", "y", "yhat")
head(df)
g <- ggplot(data = df, aes(x = Brain_Size_Species_Mean, y = yhat))
#so this entire thing does not work however I have 
```
```{r}
df <- cbind(df, ci)
names(df) <- c("x", "y", "yhat", "CIfit", "CIlwr", "CIupr")
head(df)
```
```{r}
g <- ggplot(data = df, aes(x = x, y=y))+geom_line(aes(y=CIfit, colour = "CIfit")) + geom_line(aes(y=CIlwr, colour = "CIlwr")) +geom_line(aes(y=CIupr, colour = "CIupr")) + scale_colour_manual("",values=c("CIfit" = "black", "CIupr"="blue", "CIlwr"="pink")) + xlab(" ")
g <- g + geom_point(alpha = 1/2)
g
```
```{r}
g<-lm(df)
pi <- predict(g, newdata = data.frame(a = 800), interval = "prediction", 
    level = 0.90)  # for a single value
pi
#when I search for yhat in the consule it does not come up either. 
```
#I was unable to produce PI because of R's inability to find yhat even though yhat is being used and created. For this reason I cannot evaluate whether or not I trust the model. However as far as I can tell, I would trust neither model because most of the points fall outside of the 90% confidence interval. This may however be because I removed all the na points right in the beginning because I could not get anything to work at the time. 

#From my current info available about both models, I think the log transformed on would be better because it seems that it takes into account more of the points (the untransformed g plot above has several values that completely skew the graph which do not exist in the log plot). However once I get the predicted values to work, this analysis will be easier.
